Appendix 1: Preregistered analysis with simulated data

### 2025-04-09 manuscript/manuscript.Rmd
references

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

@@

bibliography      : ["references.bib", "r-references.bib"]

csl               : vox-sanguinis.csl

@@

This manuscript uses the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCSWorkflowOpen2021] to ensure reproducibility and transparency. All code <!--and data--> are available at <!--insert repository URL-->.

This is an example of a non-essential citation [@@vanlissaWORCSWorkflowOpen2021]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

@@

>>>>

author: 
  - name          : "Abigail Edwards"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "abigail.edwards@uq.edu.au"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Mikko Arvas"
    affiliation   : "2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "The University of Queensland, Australia"
  - id            : "2"
    institution   : "Finnish Red Cross Blood Service, Finland"

@@

bibliography      : ["references.bib", "r-references.bib"]
#create with zotero using "Better Bibtex" https://retorque.re/zotero-better-bibtex/

csl               : vox-sanguinis.csl
#https://www.zotero.org/styles?q=vox

@@

This manuscript uses the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @lissaWORCSWorkflowOpen2021] to ensure reproducibility and transparency. All code <!--and data--> are available at <!--insert repository URL-->.

This is an example of a non-essential citation [@lissaWORCSWorkflowOpen2021]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

@@

<!--https://tex.stackexchange.com/questions/702678/generating-citation-keys-with-zotero-and-better-bibtex-plugin  Zotero library -> right click -> Better BibTex -> Refresh BibTex Key. Do this for each entry. Then export the collection/library as references.bib file to /manuscript folder for use with this file -->

### 2025-04-09 preregistration.Rmd
references

---
title           : "Measuring psychological ownership and identity in a Finnish blood donor context"
shorttitle      : "Donor ownership"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"

@@

@@

5.2.2025 mail from Abby

TODO:

- references

@@

Having a donor self-identity is considered a key motivational factor for sustained blood donation behaviour (Callero, 1985; Ferguson et al., 2020). Within Identity Theory, when a new donor first gives blood they develop a role-identity (I am a blood donor). As a novice donor continues to donate, this role-identity is validated, and thus blood donation becomes part of a donor’s self-identity (Being a blood donor is an important part of who I am; Grube & Piliavin, 2000; Masser, White, Hyde, Terry, & Robinson, 2009). However, despite the link between donor self-identity and donor retention, there are currently no interventions which can foster a sense of identity in donors that do not rely exclusively on repeat donation behaviour. 
Psychological ownership (this is mine) is the sense of ownership experienced over both material (e.g., blood collection agency) and abstract immaterial (e.g., blood donation behaviour) possessions (Pierce et al., 2001). The ownership volunteers experience over a non-profit organisation has been linked to sustained volunteering behaviour (Ainsworth, 2020). Further, psychological ownership is theoretically associated with identity as it has been proposed that through possession identity is established and maintained (Dittmar, 1992; Pierce et al., 2001). 
In an Australian donor context, we have provided initial support for the idea that psychological ownership experienced towards a blood collection agency both increases with past donation experience and is positively associated with blood donor self-identity (Edwards et al., 2023). Further, in a series of semi-structured interviews we have shown that Australian blood donors primarily expressed ownership over the blood donation process (role behaviour), not the blood collection agency (organisation). As such, interventions that enhance the amount of psychological ownership donors experience over their donation have the potential to impact donor retention. 
In this study we try to repeat results from Edwards et al., 2023 in Finland by collecting similar questionnaire data and analysing them with a structural equation model. We include pre-registered R analysis code for direct repetition of Edwards et al., 2023 in Appendix 1.

@@

Cross sectional survey study modelled with a structural equation model.

@@

Number of life time donations (bd02) and number of donations in last years (bd03) and likert scale measured variables (po01-3, si01-03, it01-03, ac01-04, iv01-03) will be treated as numeric. Last donation date (bd04) will transformed "bd04 / 10^-(2 - str_length(as.numeric(max(bd04))))".

@@

In supplement we will report results from all models, but as the main results we will report the model with highest Comparative Fit Index (CFI). 95 % confidence or credible intervals will be used to decide if an effect is considered significant or not.

@@

# References
## 
\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}
\noindent

>>>>

---
title           : "Measuring psychological ownership and identity in a Finnish blood donor context"
shorttitle      : "Donation ownership"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"

@@

csl             : vox-sanguinis.csl
bibliography      : ["manuscript/references.bib", "manuscript/r-references.bib"]

@@

<!-- to be submitted to https://prereg-psych.org/ >

@@

Having a donor self-identity is considered a key motivational factor for sustained blood donation behavior [@calleroRoleidentitySalience1985,@fergusonTypologyBloodDonor2020]. Within Identity Theory, when a new donor first gives blood they develop a role-identity (I am a blood donor). As a novice donor continues to donate, this role-identity is validated, and thus blood donation becomes part of a donor’s self-identity (Being a blood donor is an important part of who I am; [@grubeRoleIdentityOrganizational2000,@masserPredictingBloodDonation2009]. However, despite the link between donor self-identity and donor retention, there are currently no interventions which can foster a sense of identity in donors that do not rely exclusively on repeat donation behavior. 
Psychological ownership (this is mine) is the sense of ownership experienced over both material (e.g., blood collection agency) and abstract immaterial (e.g., blood donation behavior) possessions [@pierceTheoryPsychologicalOwnership2001]. The ownership volunteers experience over a non-profit organisation has been linked to sustained volunteering behavior [@ainsworthFeelingsOwnershipVolunteering2020]. Further, psychological ownership is theoretically associated with identity as it has been proposed that through possession identity is established and maintained [@dittmarSocialPsychologyMaterial1992, @pierceTheoryPsychologicalOwnership2001]. 
In an Australian donor context, we have provided initial support for the idea that psychological ownership experienced towards a blood collection agency both increases with past donation experience and is positively associated with blood donor self-identity [@edwardsPsychologicalOwnershipIdentity2023]. Further, in a series of semi-structured interviews we have shown that Australian blood donors primarily expressed ownership over the blood donation process (role behaviour), not the blood collection agency (organisation). As such, interventions that enhance the amount of psychological ownership donors experience over their donation have the potential to impact donor retention. 
In this study we try to repeat results from Edwards et al., 2023 in Finland by collecting similar questionnaire data from donors of Finnish Red Cross Blood Service (FRCBS) and modeling the questionnaire data with a structural equation model. We include pre-registered R analysis code for direct repetition of Edwards et al., 2023 in Appendix 1.

@@

Cross sectional survey study modeled with a structural equation model.

@@

Number of life time donations (bd02) and number of donations in last years (bd03) and likert scale measured variables (po01-3, si01-03, it01-03, ac01-04, iv01-03) will be treated as numeric. Last donation date (bd04) will transformed "bd04 / 10^-(1 - str_length(as.numeric(max(bd04))))".

@@

In supplement we will report results from all models included in preregistered analysis (Appendix 1), but as the main results we will report the model with highest Comparative Fit Index (CFI). Among models with identical CFIs we will choose the model which gives most conservative i.e. lowest estimate of ind_eff =  a1* d21 * b2. 95 % confidence or credible intervals will be used to decide if an effect is considered significant or not.

@@

# References

::: {#refs custom-style="Bibliography"}
:::

\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}
\noindent

### 2025-04-09 preregistration_code.Rmd
references

TODO:

 -remove superfluous outputs

 -check discussion with Lauri, was there anything else to do?

 -check model saving

 -fill out the preregistration form

 -are Abigail's sum score coefficients bootstrapped?

 -report effects of exclusions

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(worcs)
library(tidyverse)
library(gtsummary)
library(likert)
library(here)
library(corrplot)
library(ggstats)
library(lavaan)
library(lavaanPlot)
library(kableExtra)
#library(semPlot) # update plots to semPlot later
#library(blavaan) # could not get it to work with this model and synthetic data
#library(tidySEM) # https://github.com/yrosseel/lavaan/issues/359 lavaan does not work if tidySEM is loaded.
```

@@

```{r}
load_data()
if (exists("data_simulated")) {
  data <- data_simulated
  rm(data_simulated)
}
# sometimes it get strange errors about C stack which can be solved with this
#data <- as.data.frame(data)
fitmodels <- TRUE
if (!fitmodels) {
  print("Loading previously fitted models")
  load(file=here(str_replace(str_c("results/",datafile),"\\.data\\.",".models.")))
  fit.po02ss <- models$fit.po02ss
  fit.po02 <- models$fit.po02
  fit.po03ss <- models$fit.po03ss
  fit.po03 <- models$fit.po03
}

@@

## Age by Gender

@@

p <- ggplot(data)
p <- p +  geom_histogram(aes(x=de02),binwidth = 5)
p <- p + facet_wrap(. ~ de01)
p <- p + xlab("Age in years")
p

@@

@@

#lavaan does not understand empty factor levels
data.fit <- data %>%
  #lavaan cannot deal with unordered factor with more then 2 levels
  filter(de01 == 'man' | de01 == "women") %>% # EXCLUSION
  filter(bd01 != 'no') %>% # EXCLUSION
  mutate(
    across(isfactor, ~ fct_drop(.x)
    ) %>% 
      mutate(
        bd04 = as.numeric(bd04), # lavaan cannot handle dates
        bd04 = bd04 / 10^-(2 - str_length(as.numeric(max(bd04)))) # https://groups.google.com/g/lavaan/c/r7w-4HHg5R0 
        #"Your underweight variance seems to be much larger than other variances.  Try dividing it by 10 or 100 to make the SDs more similar across modeled variables." 
        # But this does not seem to necessarily help.
      )
  ) %>% 
  #Original paper used sum scores instead of CFA. Let's add them for comparison
  mutate(
    ss_psycown = as.numeric(po01) + as.numeric(po02) + as.numeric(po03),
    ss_selfid = as.numeric(si01) + as.numeric(si02) + as.numeric(si03),
    ss_intention = as.numeric(it01) + as.numeric(it02) + as.numeric(it03),
    #donation history is on diffent scales, normalise them before summing.
    #others should be positively correlated, but bd04 negatively
    ss_blooddonor = scale(as.numeric(bd02)) 
    + scale(as.numeric(bd01)) 
    + scale(bd03)  
    -scale(bd04) # do we want to include the DATE OF LAST DONATION?

  )

@@

```{r}
po01.model <- ' po =~ po01 + po02 + po03
                si =~ si01 + si02 + si03
                it =~ it01 + it02 + it03
                ac =~ ac01 + ac02 + ac03 + ac04
                ai =~ ai01 + ai02 + ai03 + ai04 
                iv =~ iv01 + iv02 + iv03
                bd =~ bd02 + bd03 + bd04 #bd02 is sure correlate positively

@@

fit.po01.cfa <- cfa(po01.model,  
                    estimator = "WLSMV", #

                    data = data.fit)
fit.po01.cfa
```

@@

```{r}
cfastd <- lavaan::standardizedsolution(fit.po01.cfa)
cfastd %>% 
  #"est.std" (or Std.all in above summary output) is "factor loading" and crude rule if thumb is that abs(Std.all) should be above 0.3
  filter(abs(est.std) < 0.3) %>% 
  select(-z,-se) %>% 
  arrange(abs(est.std)) %>% 
  # Just the loadings
  filter(op == '=~')
# with synthetic data bd04 should come up
# as they are just random as can be seen from the corplot
```

@@

#cfa should be better than cfa.o in all measures. cfi and chisq should be bigger, rmsea and srmr smaller in model cfa
```

@@

```{r}
varTable(fit.po02ss)
```

@@

```{r}
lavaan::standardizedsolution(fit.po02ss) %>% select(-label)
# Use standardizedSolution to obtain SEs and test statistics for standardized estimates.

```{r}
lavaan::standardizedsolution(fit.po02ss) %>% select(-label,se,z) %>%  filter(op == '~')
```

@@

lavaanPlot(
  model=fit.po02ss,  
  coefs = TRUE,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  labels = labelsforplottingnull,

  #In simulated data there should be correlations inside
  # bloodonor, psycown, selfid
  # and between
  # bloodonor, psycown
  # and nothing else
  sig = 0.001
  # if sig is < 0.001 one gets significant correlations
  # also from simulated data elsewhere suggesting that 0.05 is not enough

  ) %>% lavaanPlot::embed_plot_pdf(here("figures/plsssem01.pdf"))
```

```{r}
# Same with standardised coefficients
lavaanPlot(
  model = fit.po02ss, 
   labels = labelsforplottingnull,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  coefs = TRUE, 
  stand = TRUE,
  sig=0.001
  ) %>% lavaanPlot::embed_plot_pdf(here("figures/plsssem02.pdf"))
```

```{r}
#semPlot::semPaths(fit.po02ss)
```

@@

@@

```{r}
fit.po03ss.best <- parameterEstimates(fit.po03ss)
fit.po03ss.best %>% select(-se,-z) %>% filter(op == "~")
```

@@

```{r}
varTable(fit.po02)
```

@@

```{r}
lavaan::standardizedsolution(fit.po02) %>% select(-label)
# Use standardizedSolution to obtain SEs and test statistics for standardized estimates.

```{r}
lavaan::standardizedsolution(fit.po02) %>% select(-label,se,z) %>%  filter(op == '~')
```

@@

fit.po02.est  <-standardizedSolution(fit.po02)
fit.po02.est %>% 
  filter(abs(est.std) < 0.3) %>% 
  select(-z,-se) %>% 
  arrange(abs(est.std)) %>% 
  # Just the loadings
  filter(op != '~1')

@@

lavaanPlot(
  model=fit.po02,  
  coefs = TRUE,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  labels = labelsforplotting,

  #In simulated data there should be correlations inside
  # bloodonor, psycown, selfid
  # and between
  # bloodonor, psycown
  # and nothing else
  sig = 0.001
  # if sig is < 0.001 one gets significant correlations
  # also from simulated data elsewhere suggesting that 0.05 is not enough

  ) %>% lavaanPlot::embed_plot_pdf(here("figures/pllvsem01.pdf"))
```

```{r}
# Same with standardised coefficients
lavaanPlot(
  model = fit.po02, 
   labels = labelsforplotting,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  coefs = TRUE, 
  stand = TRUE,
  sig=0.001
  ) %>% lavaanPlot::embed_plot_pdf(here("figures/pllssem02.pdf"))
```

@@

```{r}
data.forest  <- fit.po03.best %>% 
  mutate(estmet = "Factor analysis\nbootstrapped") %>%  
  filter(op == "~" | op == ":=") %>% 
  bind_rows(
    fit.po02.est %>% mutate(estmet = "Factor analysis") %>% 
      rename(est=est.std) %>% 
      filter(op == "~"| op == ":=") 
  ) %>% 
  mutate(
    term = str_c(label,":",lhs,op,rhs)
    ) %>% 
  arrange(estmet, term)

data.forest  <- fit.po03ss.best %>% 
  mutate(estmet = "Sum score\nbootstrapped") %>%  
  filter(op == "~"| op == ":=") %>% 
  bind_rows(
    fit.po02ss.est %>% mutate(estmet = "Sum score") %>% 
      rename(est=est.std) %>% 
      filter(op == "~"| op == ":=") 
  ) %>% 
  mutate(
    term = str_c(label,":",lhs,op,rhs)
    ) %>% 
  arrange(estmet, term) %>% 
  bind_rows(data.forest) %>% 
  mutate(
    lhs =str_replace_all(lhs,"ss_",""),
    rhs =str_replace_all(rhs,"ss_",""),
    term =str_replace_all(term,"ss_",""),
    term =str_replace_all(term,"ind_eff:ind_eff:","ind_eff:"),
    estmet = as.factor(estmet),
    hollow_group=factor(if_else(ci.lower<=0 & ci.upper>=0, NA_character_, as.character(estmet)),
                             levels=levels(estmet))
  )

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(worcs)
library(tidyverse)
library(gtsummary)
library(likert)
library(here)
library(corrplot)
library(ggstats)
library(lavaan)
library(lavaanPlot)
library(kableExtra)
#library(semPlot) # update plots to semPlot later
#library(blavaan) # could not get it to work with this model and synthetic data, try as sensitivity analysis later
#library(tidySEM) # https://github.com/yrosseel/lavaan/issues/359 lavaan does not work if tidySEM is loaded!
```

@@

```{r}
load_data()
if (exists("data_simulated")) {
  data <- data_simulated
  rm(data_simulated)
}
# sometimes I get strange errors about C stack which can be solved with this
#data <- as.data.frame(data)
fitmodels <- TRUE
if (!fitmodels) {
  print("Loading previously fitted models")
  load(file=here(str_replace(str_c("results/",datafile),"\\.data\\.",".models.")))
  fit.po02ss <- models$fit.po02ss
  fit.po03ss <- models$fit.po03ss
  fit.po02 <- models$fit.po02
  fit.po03 <- models$fit.po03
}

@@

## Age by sex

@@

p <- ggplot(data %>% filter(de01 == 'man' | de01 == "women"))
p <- p +  geom_histogram(aes(x=de02),binwidth = 5)
p <- p + facet_wrap(. ~ de01)
p <- p + xlab("Age in years")
p

@@

# Exclusions

data %>%
  filter(!(de01 == 'man' | de01 == "women"))  %>% nrow()
cat("are removed because of sex\n")

data %>%
  filter(bd01 == 'no') %>% nrow()
cat("are removed because of non-eligibility\n")

data %>%
  #lavaan cannot deal with unordered factor with more then 2 levels
  filter(de01 == 'man' | de01 == "women") %>% 
  filter(bd01 != 'no') %>% nrow()
cat("in total after exclusions.\n")

@@

#lavaan does not understand empty factor levels
data.fit <- data %>%
  #lavaan cannot deal with unordered factor with more then 2 levels
  filter(de01 == 'man' | de01 == "women") %>% # EXCLUSION
  filter(bd01 != 'no') %>% # EXCLUSION
  mutate(
    across(isfactor, ~ fct_drop(.x)
    ) %>% 
      mutate(
        bd04 = as.numeric(bd04), # lavaan cannot handle dates
        bd04 = bd04 / 10^-(1 - str_length(as.numeric(max(bd04))))
        #divide the numeric date which is in 10000s by 10000
        # https://groups.google.com/g/lavaan/c/r7w-4HHg5R0 
        #"Your underweight variance seems to be much larger than other variances.  Try dividing it by 10 or 100 to make the SDs more similar across modeled variables." 
        )
  ) %>% 
  #Original paper used sum scores instead of FA. 
  mutate(
    ss_psycown = as.numeric(po01) + as.numeric(po02) + as.numeric(po03),
    ss_selfid = as.numeric(si01) + as.numeric(si02) + as.numeric(si03),
    ss_intention = as.numeric(it01) + as.numeric(it02) + as.numeric(it03)
    )

@@

```{r}
po01.model <- ' po =~ po01 + po02 + po03
                si =~ si01 + si02 + si03
                it =~ it01 + it02 + it03
                ac =~ ac01 + ac02 + ac03 + ac04
                ai =~ ai01 + ai02 + ai03 + ai04 
                iv =~ iv01 + iv02 + iv03
                bd =~ bd02 + bd03 + bd04 #bd02 is sure to correlate positively

@@

fit.po01.cfa <- cfa(po01.model,  
                    estimator = "MLR", #

                    data = data.fit2)
fit.po01.cfa
```

@@

### CFA metrics

```{r}
cfastd <- lavaan::standardizedsolution(fit.po01.cfa)
cfastd %>% 
  #"est.std" (or Std.all in above summary output) is "factor loading" and crude rule if thumb is that abs(Std.all) should be above 0.3
  filter(abs(est.std) < 0.3) %>% 
  select(-z,-se) %>% 
  arrange(abs(est.std)) %>% 
  # Just the loadings
  filter(op == '=~')
```

@@

#cfa should be better than cfa.o in all measures. 
#cfi and chisq should be bigger, rmsea and srmr smaller in model cfa
```

@@

@@

```{r}
fit.po02ss.est  <-standardizedSolution(fit.po02ss)
fit.po02ss.est %>% select(-label,se,z) %>%  filter(op == '~')
```

@@

lavaanPlot(
  model = fit.po02ss, 
   labels = labelsforplottingnull,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  coefs = TRUE, 
  stand = TRUE,
  sig=0.001
  ) %>% lavaanPlot::embed_plot_pdf(here("figures/plsssem02.pdf"))
```

@@

```{r}
fit.po03ss.best  <-standardizedSolution(fit.po03ss)
fit.po03ss.best %>% select(-label,se,z) %>%  filter(op == '~')
```

```{r}
fit.po03ss.best %>% 
  filter(abs(est.std) < 0.3) %>% 
  select(-z,-se) %>% 
  arrange(abs(est.std)) %>% 
  # Just the loadings
  filter(op != '~1')

@@

@@

@@

```{r}
fit.po02.est  <-standardizedSolution(fit.po02)
fit.po02.est %>% select(-label,se,z) %>%  filter(op == '~')
```

@@

fit.po02.est %>% 
  filter(abs(est.std) < 0.3) %>% 
  select(-z,-se) %>% 
  arrange(abs(est.std)) %>% 
  # Just the loadings
  filter(op != '~1')

@@

lavaanPlot(
  model = fit.po02, 
   labels = labelsforplotting,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  coefs = TRUE, 
  stand = TRUE,
  sig=0.001
  ) %>% lavaanPlot::embed_plot_pdf(here("figures/pllssem02.pdf"))
```

@@

```{r}
data.forest  <- fit.po03.best %>% 
  mutate(estmet = "Factor analysis\nbootstrapped") %>%  
  #rename(est=est.std) %>% 
  filter(op == "~" | op == ":=") %>% 
  bind_rows(
    fit.po02.est %>% mutate(estmet = "Factor analysis") %>% 
      rename(est=est.std) %>% 
      filter(op == "~"| op == ":=") 
  ) %>% 
  mutate(
    term = str_c(label,":",lhs,op,rhs)
    ) %>% 
  arrange(estmet, term)

data.forest  <- fit.po03ss.best %>% 
  rename(est=est.std) %>% 
  mutate(estmet = "Sum score\nbootstrapped") %>%  
  filter(op == "~"| op == ":=") %>% 
  bind_rows(
    fit.po02ss.est %>% mutate(estmet = "Sum score") %>% 
      rename(est=est.std) %>% 
      filter(op == "~"| op == ":=") 
  ) %>% 
  mutate(
    term = str_c(label,":",lhs,op,rhs)
    ) %>% 
  arrange(estmet, term) %>% 
  bind_rows(data.forest) %>% 
  mutate(
    lhs =str_replace_all(lhs,"ss_",""),
    rhs =str_replace_all(rhs,"ss_",""),
    term =str_replace_all(term,"ss_",""),
    term =str_replace_all(term,"ind_eff:ind_eff:","ind_eff:"),
    term =str_replace_all(term,"bd02","blooddonor:"),
    term =str_replace_all(term,"blooddonor:","blooddonor"),
    term =str_replace_all(term,"^:",""),
    estmet = as.factor(estmet),
    hollow_group=factor(if_else(ci.lower<=0 & ci.upper>=0, NA_character_, as.character(estmet)),
                             levels=levels(estmet))
  )
